---
title: "summarize.multi.glm"
author: "Dan Warren"
date: "January 29, 2016"
output: html_document
---
Multi-GLM Summary
=================================
***
  
***
# AUC on training data
### Rows indicate model making the prediction, columns indicate data being predicted
```{r warning=FALSE, echo=FALSE, fig.width=17, fig.height=17}
kable(multi.glm$train.pred.table, digits = 3)
```


# AUC on test data
### Rows indicate model making the prediction, columns indicate data being predicted
```{r warning=FALSE, echo=FALSE, fig.width=17, fig.height=17}
kable(multi.glm$test.pred.table, digits = 3)
```

# Spearman rank correlation, model vs. truth
### Rows indicate model making the prediction, columns indicate data being predicted
```{r warning=FALSE, echo=FALSE, fig.width=17, fig.height=17}
kable(multi.glm$truth.table, digits = 3)
```


# Models and predictions
```{r warning=FALSE, echo=FALSE, fig.width=17, fig.height=17}
print("Combined suitability, all species")
plot(multi.glm$merged.suitability)
print("Combined model, all species")
plot(multi.glm$predictions$all)

for(i in names(multi.glm$species)){
   this.sp <- i
   print(multi.glm$species[[i]]$species.name)
   print(multi.glm$species[[i]]$virtualspecies)
   par(cex = 1.5)
   plotResponse(multi.glm$species[[i]]$virtualspecies, cex=1.5)
   par(mfrow=c(1,1), cex = 1.5)
   print(multi.glm$species[[i]], print.tables=FALSE)
   points(multi.glm$species[[i]]$presence.points)
   plot(multi.glm$predictions[[i]])
}
```